Pre-Project Review

### 2021-11-19 article/article.tex
Change article style

\documentclass[sotoncolour]{uosarticle}
\graphicspath{{../figures/}}
\hypersetup{colorlinks=true}

\usepackage[
    backend=biber,
    style=phys,
    natbib=true,
    url=false, 
    doi=false,
    eprint=false,
    autocite=superscript
]{biblatex}
\addbibresource{references.bib}

\department  {School of Physics and Astronomy}
\title       {Pre-Project Review}
\modulename  {PH4111}
\authors     {180014855}
\date        {\today}

\begin{document}
\frontmatter
\maketitle
\begin{abstract}
This work is about \dots
\end{abstract}

\mainmatter

@@

\backmatter
\printbibliography
\end{document}

>>>>

\documentclass{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage[onehalfspacing]{setspace} % Correct 1.5 line spacing

\usepackage{graphicx}  % Figures
\graphicspath{{../figures/}}

\usepackage{fontspec}  % Fonts
\usepackage{helvet}
\usepackage{newpxtext,newpxmath}
\defaultfontfeatures{Scale=MatchLowercase, Ligatures=TeX}

\usepackage{url}
\usepackage{hyperref}  % Links
\usepackage{titlesec}  % Modify title/section/chapter commands
\usepackage{mathtools} % 
\usepackage{gensymb}   % \degree symbol

\usepackage{booktabs}  % \toprule, etc., in tables

\usepackage{caption}   % Caption figures
\DeclareCaptionFont{captionlabelfont}{\bfseries \sffamily}
\DeclareCaptionFont{captiontextfont}{\sffamily}
\captionsetup{labelfont=captionlabelfont, textfont=captiontextfont}

\usepackage{fancyhdr}  % Fancy header/footer
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
%\renewcommand{\headrulewidth}{0pt}

\renewcommand{\thefootnote}{\fnsymbol{footnote}} % Change footnote style

% Bibliography
\usepackage[backend=biber, style=phys, natbib=true,
			url=false, doi=false, eprint=false,
			autocite=superscript]{biblatex}
\addbibresource{references.bib}

%\department  {School of Physics and Astronomy}
\title       {Pre-Project Review}
%\modulename  {PH4111}
%\authors     {180014855}
%\date        {\today}

\begin{document}

\begin{titlepage}
	\centering
	{\includegraphics[width=0.3\textwidth]{uos-logo}}
	\par\vspace{1cm}
	{\LARGE University of St. Andrews\par}
	\vspace{1cm}
	{\Large Final year project\par}
	\vspace{1.5cm}
	{\huge\bfseries Millimetre-wave cloud profiling radar\par}
	{\huge\bfseries Pre-Project Review\par}
	\vspace{2cm}
	{\Large 180014855\par}
	{\small Word count: 2000\par}
	{\small Module: PH4111}
	\vfill

	{\large \today\par}
\end{titlepage}

\begin{abstract}
This work is about \dots
\end{abstract}

%\mainmatter

@@

%\backmatter
\printbibliography
\end{document}
